FIXME

### 2013-09-03 writeups/proposal/proposal.tex
foo
Former-commit-id: f26fb1b725bef4cd978cc37c1be1cb7a60362071 [formerly dfec040bcb0a881d28c3ac61b3b2bc12060ac413]
Former-commit-id: 54970fa7dec0e5d2e84f5f34be93ff84f9f595aa

In order to represent word order information, a funciton must be used that converts the memory vectors for a set of words (``stack $\Phi$'') into a new uncorrelated environment vector.
The BEAGLE model uses circular convolution and inverse correlation as the encoding and decoding operations.
Howerver, that is certainly not the only operation that can generate new uncorrelated vectors from a set of memory vectors.
\textcite{Sahlgren2008} used a much simpler random permutation method for this operation.

Random permutatinos use a large sparse vector of zeros with a few ones in random locations as an environment vector for each of the words.
In order to create a new vector for a particular word that occurs one back ($\mathit{stack}^{-1}$), that word's environment vector ($e_{stack}$) is bit shifted to the left one position.
This produces a new environment vector for the combination of ``stack'' and the one back position that is uncorrelated with the original ``stack'' environment vector and all other environment vectors.
So if ``stack overflow'' occurred in a sentence, the one-back environment vector for ``stack'' would be added to the memory vector for ``overflow'' ($m_{overflow} = m_{overflow'} + e_{stack^{-1}}$).

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{context} = e_{stack^{-1}}$).
The memory vector for ``overflow'' will be correlated the highest with this context vector since it contains this vector.

>>>>

In order to represent word order information, a funciton must be used that converts an environment vector for a set of words and positions (e.g., ``stack $\Phi$'') into a new uncorrelated environment vector.
The BEAGLE model uses circular convolution and inverse correlation as the encoding and decoding operations.
Howerver, that is certainly not the only operation that can generate new uncorrelated vectors from a set of memory vectors and positions.
\textcite{Sahlgren2008} used a much simpler random permutation method for this operation.

With random permutations, each word environment vector is a large sparse vector of zeros with a few $[1,-1]$s in random locations. 
In order to create a new environment vector for a word that preceded another word in a sentence, that word's environment vector is bit shifted to the left one position.
This produces a new environment vector for the combination of the word and the position that is uncorrelated with the original word's environment vector and all other environment vectors.

For example, suppose that the words ``stack overflow'' appear in a sentence, and we want to represent that ``stack'' preceded the word ``overflow''.
The ``stack'' environment vector ($e_{stack}$) is bit shifted one to the left, producing an environment vector for ``stack'' preceding a word ($e_{stack^{-1}}$).
That environment vector is then added to the memory vector for ``overflow'' ($m_{overflow} = m_{overflow'} + e_{stack^{-1}}$), so that ``overflow'' remembers that ``stack'' has preceded it in a sentence.

A retrieval for a word following ``stack'' (``stack $\Phi$'') is done by creating a memory vector out of all information in context.
In this case, assume only a single piece of order information is available, that ``stack'' precedes the word to retrieve.
So the memory vector for context is the environment vector for one-back ``stack'' ($m_{context} = e_{stack^{-1}}$).
The memory vector for ``overflow'' will be correlated the highest with this context vector since ``overflow'' contains this vector.
